\mythesistitleNOTSYNPOSIS

### 2012-01-05 src/thesis.tex
Reordered chrono.
Added amsthm and changed theorem environs to comply.
Added atbeginend commands to space theorem environs.
Added a few \def strings.

Added placeholders for a couple of definitions.

Started editing. Intro. Added a couple of definitions.

Minor edits to comply with amsthm

Spacing hacks mostly.

Trivial.
endnote flushing - TBD
Chapter 2 edited. See diff for details. Too many to remember. or maybe too little.

\usepackage{../lib/mythesislib}
\usepackage{../lib/mylatexlib}
% \usepackage{comment}         % DEBUG ONLY
\includeonly{010chap1,020chap2}
%\includeonly{0021ded}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main body Chapters
%
\include{010chap1}
\include{020chap2}
\include{030chap3}
\include{040chap4}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.
%
\begin{singlespace}
  \addcontentsline{toc}{chapter}{REFERENCES \tnote[minor]{make names
    in bib file uniform style w.r.t. firstname/initials}}

>>>>

\usepackage{../lib/mythesislib}
\usepackage{../lib/mylatexlib}
\usepackage{thesisfiguresandtables} % Code for tables are in this
                                % package if it is too long to inline
                                % in .tex file.

% \usepackage{comment}         % DEBUG ONLY
%\includeonly{020chap2}         % DEBUG ONLY 
%\includeonly{0021ded}         % DEBUG ONLY

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main body Chapters
%
\include{figuresandtables} % Load floats. No rendering.

\include{010chap1}
% turning counter reset. perhaps universal endnote counter is good?
% being schizo about it now. DECIDE! ENDNOTEMARKS DEPEND ON IT.
\setcounter{endnote}{0} % need to empty the file too. how?! -
                        % FIXED. turns out, just having notes is
                        % enough. or maybe it was fluke.
\include{020chap2}
\include{030chap3}
\include{040chap4}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.
%
\begin{singlespace}
  \addcontentsline{toc}{chapter}{REFERENCES \tnote[minor]{(i)make names
    in bib file uniform style w.r.t. firstname/initials (ii) have back
  refs - i.e. pages that cite the item.}}
